\\documentclass{article}
\\usepackage[margin=1in]{geometry}
\\begin{document}

\\section*{Supporting Information to the article}
Wangdi Wangdi. 2026. Vegetation community composition and species-environment relationships along an elevational gradient in south-central Bhutan. Journal of Vegetation Science.

\\section*{Appendix S1. Variance inflation factor screening by stratum}
Variance inflation factor results for all candidate environmental predictors in trees, shrubs, herbs, and regeneration strata used to select variables for canonical correspondence analysis.

\\section*{Appendix S2. Full PERMANOVA and dispersion outputs}
Complete PERMANOVA and dispersion test outputs by stratum and forest type, including full test statistics and permutation results.

\\section*{Appendix S3. Envfit results for all strata}
Environmental vector fitting results for NMDS ordinations across all strata, including vector directions, strengths, and permutation-based significance.

\\section*{Appendix S4. Indicator species list}
Full list of indicator species by forest type and stratum with indicator values and significance levels.

\\section*{Appendix S5. Machine-learning model parameters}
Detailed parameter settings for random forest and XGBoost models used in regeneration modelling.

\\section*{Appendix S6. Variable importance outputs}
Complete variable-importance tables for regeneration models, including ranking metrics for all predictors.

\\section*{Appendix S7. Cross-validation fold results}
Fold-level performance metrics for random forest and XGBoost models, including RMSE, MAE, and R2 by fold.

\\section*{Appendix S8. Diversity correlation matrix}
Correlation matrix for alpha diversity metrics across strata and forest types.

\\section*{Appendix S9. Beta diversity metrics}
Beta diversity estimates by forest type and stratum, including Whittaker's beta calculations.

\\section*{Appendix S10. Community matrix diagnostics}
Diagnostics for community matrices by stratum, including sparsity and sampling adequacy summaries.

\\end{document}

