\\documentclass{article}
\\usepackage[margin=1in]{geometry}
\\begin{document}

\\begin{center}
{\\LARGE Vegetation community composition and species-environment relationships along an elevational gradient in south-central Bhutan}\\par
\\vspace{1em}
Wangdi Wangdi\\textsuperscript{1}\\, https://orcid.org/0009-0007-7726-1742\\par
\\vspace{0.5em}
\\textsuperscript{1} Forest Resources Planning and Management Division, Department of Forests and Park Services, Ministry of Energy and Natural Resources, Royal Government of Bhutan, Thimphu, Bhutan\\par
\\end{center}

\\section*{Correspondence}
Wangdi Wangdi, Department of Forests and Park Services, Ministry of Energy and Natural Resources, Royal Government of Bhutan, Thimphu, Bhutan.\\par
Email: wangdiues@gmail.com\\par

\\section*{Funding information}
[TODO -- FUNDING SOURCE REQUIRED]

\\section*{Acknowledgements}
[TODO -- ACKNOWLEDGEMENTS REQUIRED]

\\section*{Author contributions}
[TODO -- AUTHOR CONTRIBUTIONS REQUIRED]

\\\section*{Data availability statement}\nThe data supporting the findings of this study are available in the Supporting Information (Appendix S1--S10). Processed community matrices and analysis outputs are archived in the project repository accompanying this submission (see 03_analysis/06_stage3 and 03_analysis/04_results for traceable outputs). A public repository with DOI will be provided upon acceptance. [TODO — INSERT DOI WHEN AVAILABLE]\\par\n\n\\section*{Ethics / permits statement}\nField sampling was conducted with permission from the Department of Forests and Park Services, Royal Government of Bhutan, under the administrative oversight of the Sarpang Forest Division. No protected or endangered species were collected or harmed. The study involved vegetation plots and non-destructive measurements only; no human participants or animal handling were involved. All activities complied with applicable national regulations and institutional policies. [TODO — INSERT PERMIT/APPROVAL ID IF APPLICABLE]\\par\n\n\\section*{Conflict of interest statement}
The author declares no conflicts of interest.

\\end{document}



